Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-08-12 man/figures/growth_changes.Rmd
update text and figures
cambiar colores figura 5

**Figure 5.** Comparison of median growth change ($GC$) following @Nowacki1997 for *Q. pyrenaica* sites. Dashed black lines indicate a threshold of 50 % of GC (see material and methods). Note that y-axes do not correspond in all of the three panels for the sake of clarity.

@@

```{r plot_caH}
pcaH <- gc_todos %>% dplyr::filter(site == 'gc_caH') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year', 
         my_ylab = '% GC', micolor = "#838B8B", limitesX = limitesX) + mismo_y +
  scale_x_continuous(breaks = xrange, position = 'bottom') + xlab('') + 
  annotate("text", x = 1990, y = 120, label = "CA-High", fontface = 2, size = 3)
```

```{r plot_caL}
pcaL <- gc_todos %>% dplyr::filter(site == 'gc_caL') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year',
         my_ylab = NULL, micolor = "#838B8B", limitesX = limitesX) +  mismo_y +
  scale_x_continuous(breaks = xrange, position = 'bottom') + xlab('Year') + 
  annotate("text", x = 1990, y = 120, label = "CA-Low", fontface = 2, size = 3) 
```

```{r plot_SJ}
psj <- gc_todos %>% dplyr::filter(site == 'gc_sj') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year', 
         my_ylab = NULL, micolor = "#838B8B", limitesX = limitesX) + 
  xlab('') + 
  scale_x_continuous(breaks = xrange, position = 'bottom') + 
  scale_y_continuous(trans = pos_neg_log, 
                     breaks=c(-1000, -500, -100, 1, 100, 500)) + 
  geom_hline(yintercept = 1,  lwd=0.2)+
  annotate("text", x = 1990, y = 440, label = "SJ", fontface = 2, size = 3)

@@

```{r plot_join}
gg <- psj + pcaH + pcaL + 
  plot_layout(ncol=1) & 
  # theme(plot.tag = element_text(size = 12, face = 2)) & 
  theme(plot.margin = margin(t=-1,r=3,b=-1,l=3, "pt"))
```

>>>>

**Figure 5.** Comparison of median growth change ($GC$) following @Nowacki1997 for *Q. pyrenaica* sites. Dashed black lines indicate a threshold of 50 % of GC (see material and methods). Note that y-axes do not correspond in all of the three panels for the sake of clarity. Error bars indicate standard error.

@@

```{r}
# azul, verde, rojo 
# CaH, CaL, SJ 
colores_den <- c("#56B4E9","#009E73","#CD5C5C")
```

```{r plot_caH}
pcaH <- gc_todos %>% dplyr::filter(site == 'gc_caH') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year', 
         my_ylab = NULL, micolor = colores_den[1], limitesX = limitesX) + mismo_y +
  scale_x_continuous(breaks = xrange, position = 'bottom') + xlab('') + 
  annotate("text", x = 1990, y = 120, label = "CA-High", fontface = 2, size = 3)
```

```{r plot_caL}
pcaL <- gc_todos %>% dplyr::filter(site == 'gc_caL') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year',
         my_ylab = '% GC', micolor = colores_den[2], limitesX = limitesX) +  mismo_y +
  scale_x_continuous(breaks = xrange, position = 'bottom') +  xlab('') +
  annotate("text", x = 1990, y = 120, label = "CA-Low", fontface = 2, size = 3) 
```

```{r plot_SJ}
psj <- gc_todos %>% dplyr::filter(site == 'gc_sj') %>% 
  plotGC(y = 'gc_md', yse = 'gc_md_se', x = 'year', 
         my_ylab = NULL, micolor = colores_den[3], limitesX = limitesX) + 
  xlab('') + xlab('Year') +
  scale_x_continuous(breaks = xrange, position = 'bottom') + 
  scale_y_continuous(trans = pos_neg_log, 
                     breaks=c(-1000, -500, -100, 1, 100, 500)) + 
  geom_hline(yintercept = 1,  lwd=0.2)+
  annotate("text", x = 1990, y = 440, label = "SJ", fontface = 2, size = 3)

@@

```{r plot_join}
gg <- pcaH + pcaL + psj + 
  plot_layout(ncol=1) & 
  # theme(plot.tag = element_text(size = 12, face = 2)) & 
  theme(plot.margin = margin(t=-1,r=3,b=-1,l=3, "pt"))
```
